---
title: "DMA_Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## DMA Analysis

This is a document that outlines the method that I use to analyze the output from a quantstrat backtest that uses the paramset function to
test multiple parameters for multiple symbols. It will load the data that was produced from .csv in the first instance as a dataframe called
stats. In this case it is the data for a dual moving average crossover trend following strategy. The variables are slow moving average, fast movng avergae and atr stoploss, which varies both stoploss distance from entry and trade size.

```{r}
date <- "2017-05-23"
stats <- read.csv(paste(getwd(),"/DMAopt",date,".csv", sep=""))
stats <- stats[,-1]
symbols <- as.character(unique(stats$Symbol))
library(ggplot2)
```

The first task is to identify the distribution of returns of the strategy over the paramter range tested.

```{r}
hist(stats$Net.Trading.PL, breaks =200,xlim = c(-100000,100000), main = paste("Average = ", mean(stats$Net.Trading.PL)))
```

This first level of analysis would seem to suggest that the strategy is profitable overall, that is, is you traded every parameter combination that was tested with equal weighting you would come out marginally on top (12% return over 10 years). The task now must be to eliminate parameter combinations in a non rendom fashion to produce data that will a) increase our confidence in the data we have obtained and b) increase average returns. Eventually, we may optimize each instrument, but only if we are clear about why we are doing this. So first let us have a look at some averages of the portfolios.

```{r}
portfolio_avg <- aggregate(stats[,c(1,2,3,6:33)],list(stats$Portfolio), mean)
```

Q1) What is the minimum number of trades that are aceptable for a back test?
Some, admitedly cursory, reading of the internet has show that there is no clear answer given to this question that has gained 
popular acceptance. Surely it cannot be number, say 30, as it will likely depend on the holding period of your trades and the time frame you are trading on. But this question must be tackled in some way, otherwise your data is going to be corrupted with data from sample with low amount of trades and give you spurious reults. Perhaps the way to go about answering this question in the first instance is to see how number of trades varies with the variables of fast moving average, slow moving average and ATR period and then compare this with net profit, profit to max drawdown and Sharpe ratio. These trade incorporate a 5 basis point per trade round trip cost. 

```{r}
qplot(data = portfolio_avg,x=atr,y=Num.Trades,facets = .~ma_slow,color=ma_fast,main="Variation of Number of Trades with Moving Averages & ATR Stoploss")
qplot(data = portfolio_avg,x=atr,y=Net.Trading.PL,facets = .~ma_slow,color=ma_fast,main="Variation of Net Trading Profit/Loss with Moving Averages & ATR Stoploss", geom=c("point","smooth"),ylim = c(-50000,150000))
qplot(data = portfolio_avg,x=atr,y=Profit.To.Max.Draw,facets = .~ma_slow,color=ma_fast, main="Variation of Profit:Maximum Drawdown with Moving Averages & ATR Stoploss",  geom=c("point","smooth"))
qplot(data = portfolio_avg,x=atr,y=Ann.Sharpe,facets = .~ma_slow,color=ma_fast,ylim = c(-10,6), main="Variation of the Annual Sharpe Ratio with Moving Averages & ATR Stoploss",  geom=c("point","smooth"))

```
Here it can be clearly observed from the first graph that the number of trades decreases with increasing moving average period (exponentially?), which is to be expected given that the shorter the moving average period the more closely they follow the price of the instrument which in turn means more volatility, more crossovers and more signals.

Related to this observation is that the closer the moving averages are to each other that more trades are performed. This is again due to the greater amount of crossover signals generated.

Less obvious is that the total profit is highest using smaller values of ATR for the stoploss. This in my opinion arises from the fact that the trades are sized such that the stoploss represents the same risk in terms of acount balance percentage. Thus when the stoploss is 2 times the ATR the trade size for that moving avergae combination the amount of units traded is higher than for the same moving average combination with the stop loss at 10 times ATR. This means that is a price trands hard in one direction without hitting the tighter stoploss, more profit will be generated.

However, as we see from the next graphs, as the stops will be hit more frequently the drawdowns that arise from being repeatedly stopped out of position will be greater for smaller stops. This leads to lower ratio of profit to maximum drawdown and Sharpe ratios.

This taken together seems to suggest some inefficiency in a simple linear scaling of trade size with atr multiple, and larger trades can be considered for larger ATR sizes.

But the main point is that larger period of the slow moving average (over 100) offer nothing in terms of superior profit opr risk adjusted returns and also have a low total amount of trades that inhibits our ability to have confidence in the data. For that reason I recommend using slow moving average period of less that 100.

Now to look at the distribution of net profit/loss for those trades.

```{r}
hist(subset(stats,ma_slow<110)$Net.Trading.PL,breaks =200,xlim = c(-100000,100000), main = paste("Average = ", mean(subset(stats,ma_slow<110)$Net.Trading.PL)))
```
OK, we have both i) increased average profit to 19% over 10 years and ii) increased our confidence in the data by eliminating sets with a low amount of data. Both pluses. Lets have a look at the previous analysis again on the subset to see if any trends become aparent.

```{r}
qplot(data = subset(portfolio_avg,ma_slow<110),x=atr,y=Num.Trades,facets = .~ma_slow,color=ma_fast)
qplot(data = subset(portfolio_avg,ma_slow<110),x=atr,y=Net.Trading.PL,facets = .~ma_slow,color=ma_fast)
qplot(data = subset(portfolio_avg,ma_slow<110),x=atr,y=Profit.To.Max.Draw,facets = .~ma_slow,color=ma_fast)
qplot(data = subset(portfolio_avg,ma_slow<110),x=atr,y=Ann.Sharpe,facets = .~ma_slow,color=ma_fast,ylim = c(-10,6))
```

Perhaps an examination of each of the symbols that are captured by these averages will help shed light on the nature of the relationship between moving average period and atr on the above parameters.

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_slow<110,],x=atr,y=Num.Trades,facets = .~ma_slow,color=ma_fast,main=paste("Variation of Number of Trades with MA & ATR for ",sym,sep="")))
  
}
```

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_slow<110,],x=atr,y=Net.Trading.PL,facets = .~ma_slow,color=ma_fast,main=paste("Variation of Net Trading PL with MA & ATR for ",sym,sep="")))
  
}
```

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_slow<110,],x=atr,y=Profit.To.Max.Draw,facets = .~ma_slow,color=ma_fast,main=paste("Variation of Profit:Maximum Drawdown with MA & ATR for ",sym,sep="")))
  
}
```

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_slow<110,],x=atr,y=Ann.Sharpe,facets = .~ma_slow,color=ma_fast,main=paste("Variation of Annual Sharpe Ratio with MA & ATR for ",sym,sep=""),ylim = c(-10,10)))
}
```


