---
title: "DMA_Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## TMA Analysis

This is a document that outlines the method that I use to analyze the output from a quantstrat backtest that uses the paramset function to
test multiple parameters for multiple symbols. It will load the data that was produced from .csv in the first instance as a dataframe called
stats. In this case it is the data for a dual moving average crossover trend following strategy. The variables are slow moving average, fast movng avergae and atr stoploss, which varies both stoploss distance from entry and trade size.

```{r}
date <- "2017-09-05"
stats <- read.csv(paste("/media/sjaoraid/strat/TMA/opt/TMACommOpt",date,".csv", sep=""))
stats <- stats[,-1]
symbols <- as.character(unique(stats$Symbol))
library(ggplot2)
```

The first task is to identify the distribution of returns of the strategy over the paramter range tested.

```{r}
hist(stats$Net.Trading.PL, breaks =200,xlim = c(-500000,1000000), main = paste("Average = ", mean(stats$Net.Trading.PL)))
```


```{r}
portfolio_avg <- aggregate(stats[,c(1,2,3,4,7:34)],list(stats$Portfolio), mean)
```

Q1) What is the minimum number of trades that are aceptable for a back test?
Some, admitedly cursory, reading of the internet has show that there is no clear answer given to this question that has gained 
popular acceptance. Surely it cannot be number, say 30, as it will likely depend on the holding period of your trades and the time frame you are trading on. But this question must be tackled in some way, otherwise your data is going to be corrupted with data from sample with low amount of trades and give you spurious reults. Perhaps the way to go about answering this question in the first instance is to see how number of trades varies with the variables of fast moving average, slow moving average and ATR period and then compare this with net profit, profit to max drawdown and Sharpe ratio. These trade incorporate a 5 basis point per trade round trip cost. 

```{r, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
qplot(data = portfolio_avg,x=atr,y=Num.Trades,facets = ma_med~ma_slow,color=ma_fast,main="Variation of Number of Trades with Moving Averages & ATR Stoploss")
qplot(data = portfolio_avg,x=atr,y=Net.Trading.PL,facets = ma_med~ma_slow,color=ma_fast,main="Variation of Net Trading Profit/Loss with Moving Averages & ATR Stoploss", geom=c("point","smooth"),ylim = c(-50000,150000))
qplot(data = portfolio_avg,x=atr,y=Profit.To.Max.Draw,facets = ma_med~ma_slow,color=ma_fast, main="Variation of Profit:Maximum Drawdown with Moving Averages & ATR Stoploss",  geom=c("point","smooth"))
qplot(data = portfolio_avg,x=atr,y=Ann.Sharpe,facets = ma_med~ma_slow,color=ma_fast,ylim = c(-10,6), main="Variation of the Annual Sharpe Ratio with Moving Averages & ATR Stoploss",  geom=c("point","smooth"))

```

```{r}
hist(subset(stats,ma_med<100)$Net.Trading.PL,breaks =200,xlim = c(-500000,500000), main = paste("Average = ", mean(subset(stats,ma_med<100)$Net.Trading.PL)))
```
OK, we have both i) increased average profit to 19% over 10 years and ii) increased our confidence in the data by eliminating sets with a low amount of data. Both pluses. Lets have a look at the previous analysis again on the subset to see if any trends become aparent.

```{r, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
qplot(data = subset(portfolio_avg,ma_med<100),x=atr,y=Num.Trades,facets = ma_med~ma_slow,color=ma_fast)
qplot(data = subset(portfolio_avg,ma_med<100),x=atr,y=Net.Trading.PL,facets = ma_med~ma_slow,color=ma_fast)
qplot(data = subset(portfolio_avg,ma_med<100),x=atr,y=Profit.To.Max.Draw,facets = ma_med~ma_slow,color=ma_fast)
qplot(data = subset(portfolio_avg,ma_med<100),x=atr,y=Ann.Sharpe,facets = ma_med~ma_slow,color=ma_fast,ylim = c(-10,6))
```

Perhaps an examination of each of the symbols that are captured by these averages will help shed light on the nature of the relationship between moving average period and atr on the above parameters.

```{r, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
for(sym in symbols){
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_med<100,],x=atr,y=Num.Trades,facets = ma_med~ma_slow,color=ma_fast,main=paste("Variation of Number of Trades with MA & ATR for ",sym,sep="")))
  
}
```

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_med<100,],x=atr,y=Net.Trading.PL,facets = ma_med~ma_slow,color=ma_fast,main=paste("Variation of Net Trading PL with MA & ATR for ",sym,sep="")))
  
}
```

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_med<100,],x=atr,y=Profit.To.Max.Draw,facets = ma_med~ma_slow,color=ma_fast,main=paste("Variation of Profit:Maximum Drawdown with MA & ATR for ",sym,sep="")))
  
}
```

```{r, message=FALSE, warning=FALSE}
for(sym in symbols){
  
  print(qplot(data = stats[stats$Symbol==sym&stats$ma_med<100,],x=atr,y=Ann.Sharpe,facets = ma_med~ma_slow,color=ma_fast,main=paste("Variation of Annual Sharpe Ratio with MA & ATR for ",sym,sep=""),ylim = c(-10,10)))
}
```


